### 2009-11-23 doc/manuals/janitor/tex_installation/installation.tex
Added warning about non-existing directories.

\begin{landscape}
\begin{table}[!h]
   \begin{center}
        \mycaption{Tags usable in \textit{arc.conf} within the section janitor.}{Tags usable in \textit{arc.conf} within the section janitor.}
	\label{tab:arc_conf_tags}
	\begin{longtable}{|p{3cm}|p{10cm}||p{10cm}|}
	\hline
	   \textbf{tag}    & \textbf{example}                      & \textbf{description}\\
        \hline
           enabled         & "1"                                   & Boolean flag which enables or disables janitor in A-REX.\\
	   uid             & "root"                                & The effective uid. \\
	   gid             & "0"                                   & The effective gid. \\
	   registrationdir & "/var/spool/nordugrid/janitor"        & Directory where we the current states of jobs are kept. \\
	   catalog         & "/var/spool/nordugrid/janitor/catalog/knowarc.rdf"& URL of the catalog containg the package information.\\
	   downloaddir     & "/var/spool/nordugrid/janitor/download" & Directory for downloads \\
	   installationdir & "/var/spool/nordugrid/janitor/runtime"& Directory for installation of packages                   \\
	   jobexpirytime   & "7200"                                & If a job is older than this, it is considered dead and assigned to be removal pending.\\
	   rteexpirytime   & "36"                                  & If a runtime environment was not used for this time, it will be assigned to be removal pending.\\
	   allow\_base     & "*"                                   & Allow rule for base packages. \\
	   deny\_base      & "debian::etch"                        & Deny rule for base packages.\\
	   allow\_rte      & "*"                                   & Allow rule for base packages. \\
	   deny\_rte       & "APPS/MATH/ELMER-5.0.2"               & Deny rule for base packages. \\
	   logconf         & "/opt/nordugrid/etc/log.conf"         & Location of the logging configuration file for janitor.\\
	\hline
	\end{longtable}
   \end{center}
\end{table}
\end{landscape}

>>>>

\begin{landscape}
\begin{table}[!h]
   \begin{center}
        \mycaption{Tags usable in \textit{arc.conf} within the section janitor.}{Tags usable in \textit{arc.conf} within the section janitor.}
	\label{tab:arc_conf_tags}
	\begin{longtable}{|p{3cm}|p{10cm}||p{10cm}|}
	\hline
	   \textbf{tag}    & \textbf{example}                      & \textbf{description}\\
        \hline
           enabled         & "1"                                   & Boolean flag which enables or disables janitor in A-REX.\\
	   uid             & "root"                                & The effective uid. \\
	   gid             & "0"                                   & The effective gid. \\
	   registrationdir & "/var/spool/nordugrid/janitor"        & Directory where we the current states of jobs are kept. \\
	   catalog         & "/var/spool/nordugrid/janitor/catalog/knowarc.rdf"& URL of the catalog containing the package information.\\
	   downloaddir     & "/var/spool/nordugrid/janitor/download" & Directory for downloads \\
	   installationdir & "/var/spool/nordugrid/janitor/runtime"& Directory for installation of packages                   \\
	   jobexpirytime   & "7200"                                & If a job is older than this, it is considered dead and assigned to be removal pending.\\
	   rteexpirytime   & "36"                                  & If a runtime environment was not used for this time, it will be assigned to be removal pending.\\
	   allow\_base     & "*"                                   & Allow rule for base packages. \\
	   deny\_base      & "debian::etch"                        & Deny rule for base packages.\\
	   allow\_rte      & "*"                                   & Allow rule for base packages. \\
	   deny\_rte       & "APPS/MATH/ELMER-5.0.2"               & Deny rule for base packages. \\
	   logconf         & "/opt/nordugrid/etc/log.conf"         & Location of the logging configuration file for janitor.\\
	\hline
	\end{longtable}
   \end{center}
\end{table}
\end{landscape}

It should be noted that the downloaddir or the installationdir specified
in arc.conf could be any directory. Those will not be prepared by the
package for the Linux distribution but need be created by the administrator
manually after the Janitor has been installed. This also holds for the
catalog.
